---
title: "Diamonds Analysis"
output:
  html_document:
    fig_caption: false
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 3
---


```{r setup, include=FALSE, echo=FALSE}
library(tidyverse)
library(rio)
library(Hmisc)
library(knitr)
library(DT)
library(dplyr)

#library(shiny)

```

## Exercise 8.1 (Import and Examine)
```{r output="asis", echo=FALSE}
jems <- read_csv("data/diamonds.csv")
jems %>%
       kable()

```

## Exercise 8.2 (Counting individual groups)
#### How many diamonds with a clarity of category “IF” are present in the data-set? 

```{r , echo=FALSE}
clarity <- jems %>%
  filter(clarity =="IF")
nrow(clarity)

```
####  What fraction of the total do they represent?

```{r, echo=FALSE}
fraction <-nrow(clarity)/nrow(jems)
fraction
```

## Exercise 8.3 (Summarizing proportions)
####  What proportion of the whole is made up of each category of clarity?
```{r output="asis", echo=FALSE}
jems %>%
  group_by(clarity) %>%
  count() %>%
  mutate(prop=n/nrow(jems))%>%
       datatable()
```


## Exercise 8.4 (Find specific diamonds prices)
####  What is the cheapest diamond price overall?
```{r, echo=FALSE}
min(jems$price)
```

####  What is the range of diamond prices?
```{r, echo=FALSE}
range(jems$price)
```

####  What is the average diamond price in each category of cut and color?
```{r output="asis", echo=FALSE}
jems %>% 
  group_by(cut, color) %>%
  summarise(avg = mean(price)) %>%
         datatable()
```

## Exercise 8.5 (Basic plotting)
```{r,  echo=FALSE}
jems %>%
  group_by(carat) 
ggplot(jems, aes(carat,price )) +
  geom_jitter()
```

## Exercise 8.6 (Applying transformations)
```{r }
jems <- jems %>%
  mutate(price_log10 = log10(jems$price),
         carat_log10<-log10(jems$carat))
# alternative 
jems$price_log10 <- log10(jems$price)
jems$carat_log10 <-log10(jems$carat)
```

####  Plot the transformed varibles
```{r,  echo=FALSE}
ggplot(jems, aes(x = carat_log10,y = price_log10 )) +
  geom_point()+
  geom_smooth(method = lm, se = FALSE ,colour = "red")
```

## Exercise 8.7 (Basic plotting)
```{r, echo=FALSE}
jems %>%
  group_by(carat)
ggplot(jems, aes(carat_log10,price_log10 )) +
  geom_jitter()
```

## Exercise 8.8 (Viewing models)
```{r,  echo=FALSE}
# our produce model x ~ y
diamonds_lm <- lm( price_log10 ~ carat_log10, data = jems)
diamonds_lm
diamonds_lm$coefficients %>%
     kable()
  
```

## Exercise 8.9 (Displaying models)
```{r output="asis" ,echo=FALSE}
ggplot(jems, aes( x = carat_log10, y = price_log10)) + 
  geom_point() +
  geom_smooth(method = lm, se = FALSE ,colour = "red")
```





