---
title: "Google Play Store Apps Analysis"
author: "*Wejdan Saleh*"
date: "*10/09/2020*"
output: html_document

---

```{r setup, include=FALSE, echo=FALSE}
library(tidyverse)
library(rio)
library(Hmisc)
library(knitr)
library(DT)
library(dplyr)
AppStore <- read_csv("data/googleplaystore.csv")

```


## General Information
##### Each app (row) has values for App name, catergory, rating, Reviews,Installs, Type, and more Information..

```{r  echo=FALSE}


AppStore_t <- AppStore %>%
  pivot_longer(-c(App, Category, Rating, Reviews, Installs, Type), 
               names_to = "More Information")


```

```{r echo=FALSE, }
AppStore_st <- sample_n(AppStore_t, 20)
AppStore_st %>%
  datatable()
```


## The Most popular category:

```{r echo=FALSE}

AppStore_st %>%
  group_by(Category) %>%
  summarise(n = length(Category), .groups = "drop") %>%
  datatable()

```

```{r echo=FALSE}


# Most popular Category has Install 
# Create the function 
getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}
v <- AppStore_st$Category
popular_Category <- getmode(v)
  
popular_Category
  
```

##  Count Free app VS Paid App:

### Free App ..

```{r echo=FALSE}
summarise(AppStore_st, Free_App = nrow(subset(AppStore_st,Type == "Free")) ) %>%
  datatable()

```


### Paid App ..

```{r echo=FALSE}
summarise(AppStore_st, Paid_App = nrow(subset(AppStore_st,Type != "Free")) ) %>%
  datatable()

```


## App with  highest and lowest rating:
 
### App with highest rating..
  
```{r echo=FALSE}
AppStore_st[which.max(AppStore_st$Rating),] %>%
    kable()
```
  
  
### App with Lowest rating..
  
```{r echo=FALSE}
AppStore_st[which.min(AppStore_st$Rating),] %>%
    kable()
```


## App with highest and lowest reviews:

### App with highest reviews..
```{r echo=FALSE}

AppStore_st[AppStore_st$Reviews == max(AppStore_st$Reviews),]%>%
   kable()
```


### App with lowest reviews..

```{r echo=FALSE}

AppStore_st[AppStore_st$Reviews == min(AppStore_st$Reviews),]%>%
   kable()
```


## Mean and SD for reviews:

```{r echo=FALSE}
summarise(AppStore_st, AppStore_mean = mean(Reviews, na.rm = T)) %>%
  kable()


 summarise(AppStore_st, AppStore_sd = sd(Reviews, na.rm = T)) %>%
   kable()
```


## Plots

### The Reviews and Installs BoxPlot digram..
The diagram is shows the relationship between the Reviews and Installs, when the reviews is high then the number of installation besom high.

```{r echo=FALSE}
ggplot(AppStore_st, aes(Installs, Reviews )) +
 geom_boxplot()

```


### The Reviews and Installs jitter digram..

Other diagram explain the relationship between the Reviews and Installs.

  
```{r echo=FALSE}
ggplot(AppStore_st, aes(Installs, Reviews )) +
geom_jitter(width = 0.15) 
```
 
  
## Inferential Statistics

#### The one-way ANOVA summary:

```{r echo=FALSE}
AppStore_lm <- lm( Reviews ~  Installs, data = AppStore_st)

anova(AppStore_lm) %>%
  datatable()
```


 
 